Thesis Meeting

### 2020-09-20 thesis meeting sept21.Rmd
including graph sketches for the two potential figures from different project directions

@@

```{r, echo=FALSE}
knitr::include_graphics("images/kroeker_fig1.png")
```

@@

* Driving question(s):
  + Is there a differential response at different levels of organization to variation in each of these variables 
  +	How do non-linear and linear response variables respond to stochastic vs. predictable variation?
      + look at a couple different environmental variables and how different manipulations of those variables coincides with either linear or non-linear response variables
* Potential response variables:
    + Individual: metabolic rate, growth rate, respiration rate (MMR)?
    + Population: population growth rate, population density, carrying capacity
    + Community: biomass?, NPP? Other rate based metrics?
* Potential outcome: a better understanding of these metrics that covary may not necessarily covary in their responses to variation across different levels of organization?
```{r, echo=FALSE}
knitr::include_graphics("images/kroeker_fig1.png")
```

@@

Figure 1 somewhat addresses what I wanted to accomplish with an NMDS plot, but I think it a good jumping off place for thinking about how to design search terms and contextualize environmental variability bodies of literature

```{r, fig.width=5, fig.height=5, echo=FALSE}
knitr::include_graphics("images/kroeker_fig1.png")
```

@@

# Next steps and questions 
* Is the world predicted to become more variable or more autocorrelated? 
    + And if the answer is both, how do they interact? 
    + Is it that while the world will become more like its surrounding conditions, those conditions will increase in amplitude or become more severe?

* How do I properly use ISI advanced searches to get narrower results?
* How do I accumulate the right amount of keywords to accomplish this?
* What is the right scope for the two proposed detailed questions for this thesis project?

>>>>

\newpage

@@

```{r, echo=FALSE}
knitr::include_graphics("images/option1_projprop.png")
```

\newpage

@@

* Driving question(s):
  + Is there a differential response at different levels of organization to variation in each of these variables 
  +	How do non-linear and linear response variables respond to stochastic vs. predictable variation?
      + look at a couple different environmental variables and how different manipulations of those variables coincides with either linear or non-linear response variables
* Potential response variables:
    + Individual: metabolic rate, growth rate, respiration rate (MMR)?
    + Population: population growth rate, population density, carrying capacity
    + Community: biomass?, NPP? Other rate based metrics?
* Potential outcome: a better understanding of these metrics that covary may not necessarily covary in their responses to variation across different levels of organization?

```{r, echo=FALSE}
knitr::include_graphics("images/option2_projprop.png")
```

@@

Figure 1 in Kroeker et al 2020 somewhat addresses what I wanted to accomplish with an NMDS plot, but I think it is a good jumping off place for thinking about how to design search terms and contextualize environmental variability bodies of literature

@@

\newpage
# Next steps and questions 
* Is the world predicted to become more variable or more autocorrelated? 
    + And if the answer is both, how do they interact? 
    + Is it that while the world will become more like its surrounding conditions, those conditions will increase in amplitude or become more severe?
* How do I properly use ISI advanced searches to get narrower results?
* How do I accumulate the right amount of keywords to accomplish this?
* What is the right scope for the two proposed detailed questions for this thesis project?
